Proposal: Evaluating the Impact of 2023 MLB Rule Changes on Performance Metrics and Strategies in Major League Baseball

### 2023-10-10 proposal/proposal.tex
finished discussion section of proposal

\paragraph{Discussion}

>>>>

\paragraph{Discussion}
The most challenging aspect of this research project will be accounting for 
confounding factors such as changes in player rosters which might influence the
observed differences in the metrics. This goes hand in hand with the limitations
which include the assumption that the observed differences are solely attributable
to the rule changes, without considering other external factors. Another limitation
is the amount of work done on this topic, as the rule changes were just implemented
in 2023. There are some articles that I can reference such as ..ref.. and 
..ref.. that talk about the effects of the rule changes, but no scholarly papers
have been posted about it yet. I will have to research more about statistical
papers dedicated to analyzing changes with MLB stats between seasons, in general.

If challenges arise, a fall back plan will involve conducting sensitivity analyses
and exploring alternative statistical tests/visualizations. All in all, I believe
this paper will be a great resource to show the impact of the rule changes on 
the game of baseball.
